Inequality in socioemotional skills: a cross-cohort comparison

### 2019-07-02 codes/R/paper/seskills_jpube_rev.Rnw
add funding acknowledgement

\scriptsize{Corresponding Author: Orazio Attanasio, Department of Economics, University College London,
Gordon Street, London WC1H0AX, UK. Email: o.attanasio@ucl.ac.uk. We thank participants to the NBER/LSE Trans-Atlantic Public Economics Seminar (TAPES) and our two discussants Hilary Hoynes and Gabriel Ulyssea for excellent comments. We're especially thankful to George Ploubidis for his guidance in the early stages of the project. This work is based on data from the British Cohort Study and the Millennium Cohort Study. We are grateful to The Centre for Longitudinal Studies, UCL Institute of Education, for the collection of the data, and to the UK Data Archive and UK Data Service for making them available. However, they bear no responsibility for the analysis or interpretation of the data. We would like to thank all cohort members and their families, who generously gave their time to participate in the surveys. We thank the DynaHEALTH consortium (H2020–633595 DynaHEALTH) for funding and support. GM is funded by an Economics and Social Research Council scholarship.}
\end{titlepage}

>>>>

\scriptsize{Corresponding Author: Orazio Attanasio, Department of Economics, University College London,
Gordon Street, London WC1H0AX, UK. Email: o.attanasio@ucl.ac.uk. We thank participants to the NBER/LSE Trans-Atlantic Public Economics Seminar (TAPES) and our two discussants Hilary Hoynes and Gabriel Ulyssea for excellent comments. We're especially thankful to George Ploubidis for his guidance in the early stages of the project. This work is based on data from the British Cohort Study and the Millennium Cohort Study. We are grateful to The Centre for Longitudinal Studies, UCL Institute of Education, for the collection of the data, and to the UK Data Archive and UK Data Service for making them available. However, they bear no responsibility for the analysis or interpretation of the data. We would like to thank all cohort members and their families, who generously gave their time to participate in the surveys. This project has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement No 695300 - HKADeC - ERC-2015-AdG/ERC-2015-AdG. We also thank the DynaHEALTH consortium (H2020–633595 DynaHEALTH) for funding and support. GM is funded by an Economics and Social Research Council scholarship.}
\end{titlepage}
